---
title: "HW4_Problem2"
author: "Haoyang Wang"
date: "2022-10-29"
output:
  html_document:
    toc: true
    toc_float: true
---
#load packages
```{r}
library(tidyverse)
library(p8105.datasets)
library(plotly)
```

#filter dataset with variables boro, cuisine_description, inspection_date, score, grade only
```{r}
data("rest_inspec")
nyc_restaurant = rest_inspec %>% 
  select(boro, cuisine_description, inspection_date, score, grade) %>% 
  filter(.data = ., boro == "MANHATTAN") %>% 
  na.omit()
```

#make a bar plot with count of different types of restaurant
```{r}
nyc_restaurant %>% 
  count(cuisine_description) %>% 
  mutate(cuisine_description = fct_reorder(cuisine_description, n)) %>% 
  plot_ly(
    x = ~cuisine_description, y = ~n, color = ~cuisine_description, type = "bar",
    colors = "viridis"
  )
```

#make a box plot with the score of different types of restaurant
```{r}
nyc_restaurant %>% 
  mutate(cuisine_description = fct_reorder(cuisine_description, score)) %>% 
  plot_ly(y = ~score, color = ~cuisine_description, type = "box", colors = "viridis")
```

#make a bar plot with the grade of different types of restaurant
```{r}
nyc_restaurant %>% 
  group_by(cuisine_description, grade) %>% 
  summarize(count = n()) %>% 
  plot_ly(
    y = ~count, x = ~cuisine_description, color = ~grade, 
    type = "bar", colors = "viridis"
  )
```

#make a scatter plot with the score of different types of restaurant across years
```{r}
nyc_restaurant %>% 
  mutate(inspection_date = as.Date(inspection_date)) %>%
  plot_ly(
    x = ~inspection_date, y = ~score, type = "scatter", mode = "markers",
    color = ~cuisine_description, alpha = 0.5
  )
```

#load package flexdashboard
```{r}
library(flexdashboard)
```

